Streaming CityJSON datasets

### 2024-05-03 paper/main.tex
Postgres rewrite

\begin{figure*}
  \centering
  \begin{subfigure}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/compression_random.pdf}
    \caption{}%
  \label{fig:compression_random}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/compression_adjacent.pdf}
    \caption{}%
  \label{fig:compression_adjacent}
  \end{subfigure}
  \caption{Compression factor of CityJSONSeq files for different synthetic datasets. \textbf{(a)} Based on the number of buildings; the buildings are stored as simple cuboid that are randomly generated. \textbf{(b)} Based on the percentage of shared vertices. The same cuboid buildings are used, but we locate them adjacent to each others to create shared vertices.}%
\label{fig:compression}
\end{figure*}

@@

It should be noticed that the CityJSON specification does not prescribe the storage of CityJSONSeq, only the structure of a CityJSONSeq stream.
In practice, CityJSONSeq can be stored in a variety of ways, for instance in a single file, each feature in a separate file, in a database, etc.
The optimal storage solution depends on the implementing application.
As a concrete example, we have implemented CityJSONSeq in the PostgreSQL database, using \emph{cjdb}~\citep{Powalka23}, to store independently one feature per row in the database.
Additionally, in order to facilitate pagination, CityJSONSeq is the return format of the 3DBAG API\footnote{\url{https://api.3dbag.nl/}}, which contains all buildings in the Netherlands with detailed roofs~\citep{Peters22}.

>>>>

\begin{figure*}
  \centering
  \begin{subfigure}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/compression_random.pdf}
    \caption{}%
  \label{fig:compression_random}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/compression_adjacent.pdf}
    \caption{}%
  \label{fig:compression_adjacent}
  \end{subfigure}
  \caption{Compression factor of CityJSONSeq files for different synthetic datasets. \textbf{(a)} Based on the number of buildings; the buildings are stored as simple cuboids that are randomly generated. \textbf{(b)} Based on the percentage of shared vertices; the same cuboid buildings are used, but we position them adjacent to each others to create shared vertices.}%
\label{fig:compression}
\end{figure*}

@@

It should be noticed that the CityJSON specification does not prescribe the storage of CityJSONSeq, only the structure of a CityJSONSeq stream.
In practice, CityJSONSeq can be stored in a variety of ways, for instance in a single file, each feature in a separate file, in a database, etc.
The optimal storage solution depends on the implementing application.
As a concrete example, CityJSONSeq is used by \emph{cjdb}~\citep{Powalka23}, an importer/exporter tool that stores one feature per row in PostgresSQL.
Additionally, in order to facilitate pagination, CityJSONSeq is the return format of the 3DBAG API\footnote{\url{https://api.3dbag.nl/}}, which contains all 10 million buildings in the Netherlands with detailed roofs~\citep{Peters22}.
